Security vs. Maintainability: Fixing Vulnerabilities Obfuscates your Code

### 2019-01-28 paper/ICPC19/icpc19.tex
fixing first paragraph

\section{Motivation and Research Questions}\label{sec:motivation}

\Sof{@todo: Improve this paragraph}Under the rush of companies trying to outdo each other and due to the lack of expertise in the security field, security flaws are usually detected only when hackers exploit them which happens
because developers create buggy software without knowing. Gladly, fixing these
issues usually is as simple as changing the software codebase. However,
these refactorings can sometimes have a negative impact on software maintenance, not
only because developers are under the rush of "protecting" their software but also because 
they tend to take the easiest path and not the most efficient one. Thus, we
want to understand how security refactorings impact the maintainability of software.

>>>>

\section{Motivation and Research Questions}\label{sec:motivation}
%
Due to time-to-market pressure and the lack of security expertise, code-related
security flaws are generally detected \textit{after the fact}, i.e., when
hackers exploit them. It turns out that fixing these issues is as simple as
modifying the software codebase. However, these refactorings may have a negative
impact on software maintenance, mostly because developers follow the quickest
solution to fix the problem and not necessarily the most elegant one. Thus, we
want to understand how security refactorings impact the maintainability of
software.
